AHABus \& FCORE: A Modular Bus System for High-Altitude Balloon Missions

### 2017-04-24 appendices.tex
Fix encoding format in appendix C

  \begin{itemize}
  \item
    AHABus platform's latitude in decimal format at the time the packet
    was encoded, in (8.24) fixed point format,
  \item
    AHABus platform's longitude in decimal format at the time the packet
    was encoded, in (8.24) fixed point format,
  \item
    AHABus platform's altitude in metres at the time the packet was
    encoded, in 16-bit unsigned integer format.
  \end{itemize}
\end{itemize}

>>>>

  \begin{itemize}
  \item
    AHABus platform's latitude in decimal format at the time the packet
    was encoded as a 32-bit signed integer, multiplied by 10000,
  \item
    AHABus platform's longitude in decimal format at the time the packet
    was encoded as a 32-bit signed integer, multiplied by 10000,
  \item
    AHABus platform's altitude in metres at the time the packet was
    encoded, in 16-bit unsigned integer format.
  \end{itemize}
\end{itemize}
